### 2020-06-21 backup/ncov_b2.tex
done

\bibliography{ncov_abbr}

>>>>

\begin{thebibliography}{}

\bibitem[\protect\citeauthoryear{Andersen, Rambaut, Lipkin, Holmes, and
  Garry}{Andersen et~al.}{2020}]{andersen2020proximal}
Andersen, K.~G., A.~Rambaut, W.~I. Lipkin, E.~C. Holmes, and R.~F. Garry
  (2020).
\newblock The proximal origin of {SARS-CoV-2}.
\newblock {\em Nat Med\/}~{\em 26\/}(4), 450--452.

\bibitem[\protect\citeauthoryear{Anderson and May}{Anderson and
  May}{1991}]{anderson1991infectious}
Anderson, R.~M. and R.~M. May (1991).
\newblock {\em Infectious diseases of humans: dynamics and control}.
\newblock Oxford University Press.

\bibitem[\protect\citeauthoryear{Barton, Alberti, Ames, Atkinson, Bales, Burke,
  Chen, Diallo, Earn, Fath, et~al.}{Barton et~al.}{2020}]{barton2020call}
Barton, C.~M., M.~Alberti, D.~Ames, J.-A. Atkinson, J.~Bales, E.~Burke,
  M.~Chen, S.~Y. Diallo, D.~J. Earn, B.~Fath, et~al. (2020).
\newblock Call for transparency of {COVID-19} models.
\newblock {\em Science\/}~{\em 368\/}(6490), 482--483.

\bibitem[\protect\citeauthoryear{Bedford, Neher, Hadfield, Hodcroft, Ilcisin,
  and M{\"u}ller}{Bedford et~al.}{2020}]{bedfordncov}
Bedford, T., R.~Neher, J.~Hadfield, E.~Hodcroft, M.~Ilcisin, and N.~M{\"u}ller
  (2020).
\newblock {Genomic analysis of nCoV spread. Situation report 2020-01-23.}
\newblock \url{https://nextstrain.org/narratives/ncov/sit-rep/2020-01-23}.
  Accessed 24, January, 2020.

\bibitem[\protect\citeauthoryear{Britton and Scalia~Tomba}{Britton and
  Scalia~Tomba}{2019}]{britton2019estimation}
Britton, T. and G.~Scalia~Tomba (2019).
\newblock Estimation in emerging epidemics: Biases and remedies.
\newblock {\em J R Soc Interface\/}~{\em 16\/}(150), 20180670.

\bibitem[\protect\citeauthoryear{Champredon and Dushoff}{Champredon and
  Dushoff}{2015}]{champredon2015intrinsic}
Champredon, D. and J.~Dushoff (2015).
\newblock Intrinsic and realized generation intervals in infectious-disease
  transmission.
\newblock {\em Proc R Soc Lond B Biol Sci\/}~{\em 282\/}(1821), 20152026.

\bibitem[\protect\citeauthoryear{Diekmann, Heesterbeek, and Metz}{Diekmann
  et~al.}{1990}]{diekmann1990definition}
Diekmann, O., J.~A.~P. Heesterbeek, and J.~A. Metz (1990).
\newblock On the definition and the computation of the basic reproduction ratio
  $\mathcal{R}_0$ in models for infectious diseases in heterogeneous
  populations.
\newblock {\em J Math Biol\/}~{\em 28\/}(4), 365--382.

\bibitem[\protect\citeauthoryear{Elderd, Dukic, and Dwyer}{Elderd
  et~al.}{2006}]{elderd2006uncertainty}
Elderd, B.~D., V.~M. Dukic, and G.~Dwyer (2006, October).
\newblock Uncertainty in predictions of disease spread and public health
  responses to bioterrorism and emerging diseases.
\newblock {\em Proc Natl Acad Sci USA\/}~{\em 103\/}(42), 15693 --15697.

\bibitem[\protect\citeauthoryear{Fisman, Hauck, Tuite, and Greer}{Fisman
  et~al.}{2013}]{fisman2013idea}
Fisman, D.~N., T.~S. Hauck, A.~R. Tuite, and A.~L. Greer (2013).
\newblock {An IDEA for short term outbreak projection: nearcasting using the
  basic reproduction number}.
\newblock {\em PloS One\/}~{\em 8\/}(12).

\bibitem[\protect\citeauthoryear{Flaxman, Mishra, Gandy, Unwin, Coupland,
  Mellan, Zhu, Berah, Eaton, Guzman, Schmit, Callizo, Team, Whittaker,
  Winskill, Xi, Ghani, Donnelly, Riley, Okell, Vollmer, Ferguson, and
  Bhatt}{Flaxman et~al.}{2020}]{flaxman2020estimating}
Flaxman, S., S.~Mishra, A.~Gandy, H.~J.~T. Unwin, H.~Coupland, T.~A. Mellan,
  H.~Zhu, T.~Berah, J.~W. Eaton, P.~N.~P. Guzman, N.~Schmit, L.~Callizo, I.~C.
  C.-.~R. Team, C.~Whittaker, P.~Winskill, X.~Xi, A.~Ghani, C.~A. Donnelly,
  S.~Riley, L.~C. Okell, M.~A.~C. Vollmer, N.~M. Ferguson, and S.~Bhatt (2020).
\newblock Estimating the number of infections and the impact of
  non-pharmaceutical interventions on covid-19 in 11 european countries.
\newblock
  \url{https://www.imperial.ac.uk/mrc-global-infectious-disease-analysis/covid-19/report-13-europe-npi-impact/}.
  Accessed May 4, 2020.

\bibitem[\protect\citeauthoryear{Gelman et~al.}{Gelman
  et~al.}{2006}]{gelman2006prior}
Gelman, A. et~al. (2006).
\newblock {Prior distributions for variance parameters in hierarchical models
  (comment on article by Browne and Draper)}.
\newblock {\em Bayesian analysis\/}~{\em 1\/}(3), 515--534.

\bibitem[\protect\citeauthoryear{Gelman, Rubin, et~al.}{Gelman
  et~al.}{1992}]{gelman1992inference}
Gelman, A., D.~B. Rubin, et~al. (1992).
\newblock Inference from iterative simulation using multiple sequences.
\newblock {\em Stat Sci\/}~{\em 7\/}(4), 457--472.

\bibitem[\protect\citeauthoryear{He, Lau, Wu, Deng, Wang, Hao, Lau, Wong, Guan,
  Tan, et~al.}{He et~al.}{2020}]{he2020temporal}
He, X., E.~H. Lau, P.~Wu, X.~Deng, J.~Wang, X.~Hao, Y.~C. Lau, J.~Y. Wong,
  Y.~Guan, X.~Tan, et~al. (2020).
\newblock Temporal dynamics in viral shedding and transmissibility of
  {COVID-19}.
\newblock {\em Nat Med\/}, 1--4.

\bibitem[\protect\citeauthoryear{Hethcote, Zhien, and Shengbing}{Hethcote
  et~al.}{2002}]{hethcote2002effects}
Hethcote, H., M.~Zhien, and L.~Shengbing (2002).
\newblock Effects of quarantine in six endemic models for infectious diseases.
\newblock {\em Math Biosci\/}~{\em 180\/}(1-2), 141--160.

\bibitem[\protect\citeauthoryear{Huang, Wang, Li, Ren, Zhao, Hu, Zhang, Fan,
  Xu, Gu, et~al.}{Huang et~al.}{2020}]{huang2020clinical}
Huang, C., Y.~Wang, X.~Li, L.~Ren, J.~Zhao, Y.~Hu, L.~Zhang, G.~Fan, J.~Xu,
  X.~Gu, et~al. (2020).
\newblock {Clinical features of patients infected with 2019 novel coronavirus
  in Wuhan, China}.
\newblock {\em Lancet\/}~{\em 395\/}(10223), 497--506.

\bibitem[\protect\citeauthoryear{Imai, Cori, Dorigatti, Baguelin, Donelly,
  Riley, and Ferguson}{Imai et~al.}{2020}]{imaincov}
Imai, N., A.~Cori, I.~Dorigatti, M.~Baguelin, C.~A. Donelly, S.~Riley, and
  N.~M. Ferguson (2020).
\newblock {Report 3: Transmissibility of 2019-nCoV}.
\newblock
  \url{https://www.imperial.ac.uk/media/imperial-college/medicine/sph/ide/gida-fellowships/Imperial-2019-nCoV-transmissibility.pdf}.
  Accessed 26, January, 2020.

\bibitem[\protect\citeauthoryear{Imai, Dorigatti, Cori, Donelly, Riley, and
  Ferguson}{Imai et~al.}{2020}]{imaincov0}
Imai, N., I.~Dorigatti, A.~Cori, C.~A. Donelly, S.~Riley, and N.~M. Ferguson
  (2020).
\newblock {Report 2: Estimating the potential total number of novel Coronavirus
  cases in Wuhan City, China}.
\newblock
  \url{https://www.imperial.ac.uk/media/imperial-college/medicine/sph/ide/gida-fellowships/2019-nCoV-outbreak-report-22-01-2020.pdf}.
  Accessed 3, February, 2020.

\bibitem[\protect\citeauthoryear{King, Domenech~de Cell{\`e}s, Magpantay, and
  Rohani}{King et~al.}{2015}]{king2015avoidable}
King, A.~A., M.~Domenech~de Cell{\`e}s, F.~M. Magpantay, and P.~Rohani (2015).
\newblock Avoidable errors in the modelling of outbreaks of emerging pathogens,
  with special reference to {Ebola}.
\newblock {\em Proc R Soc Lond B Biol Sci\/}~{\em 282\/}(1806), 20150347.

\bibitem[\protect\citeauthoryear{Lauer, Grantz, Bi, Jones, Zheng, Meredith,
  Azman, Reich, and Lessler}{Lauer et~al.}{2020}]{lauer2020incubation}
Lauer, S.~A., K.~H. Grantz, Q.~Bi, F.~K. Jones, Q.~Zheng, H.~R. Meredith, A.~S.
  Azman, N.~G. Reich, and J.~Lessler (2020).
\newblock {The incubation period of coronavirus disease 2019 (COVID-19) from
  publicly reported confirmed cases: estimation and application}.
\newblock {\em Ann Intern Med\/}.

\bibitem[\protect\citeauthoryear{Li, Guan, Wu, Wang, Zhou, Tong, Ren, Leung,
  Lau, Wong, et~al.}{Li et~al.}{2020}]{li2020early}
Li, Q., X.~Guan, P.~Wu, X.~Wang, L.~Zhou, Y.~Tong, R.~Ren, K.~S. Leung, E.~H.
  Lau, J.~Y. Wong, et~al. (2020).
\newblock Early transmission dynamics in {Wuhan, China}, of novel
  coronavirus--infected pneumonia.
\newblock {\em N Engl J Med\/}.

\bibitem[\protect\citeauthoryear{Liu, Hu, Kang, Lin, Zhong, Xiao, He, Song,
  Huang, Rong, Deng, Zeng, Tan, Zeng, Zhu, Li, Wan, Lu, Deng, He, and Ma}{Liu
  et~al.}{2020}]{liuncov}
Liu, T., J.~Hu, M.~Kang, L.~Lin, H.~Zhong, J.~Xiao, G.~He, T.~Song, Q.~Huang,
  Z.~Rong, A.~Deng, W.~Zeng, X.~Tan, S.~Zeng, Z.~Zhu, J.~Li, D.~Wan, J.~Lu,
  H.~Deng, J.~He, and W.~Ma (2020).
\newblock {Transmission dynamics of 2019 novel coronavirus (2019-nCoV)}.
\newblock \url{https://www.biorxiv.org/content/10.1101/2020.01.25.919787v1}.
  Accessed 27, January, 2020.

\bibitem[\protect\citeauthoryear{Liu, Gayle, Wilder-Smith, and Rockl{\"o}v}{Liu
  et~al.}{2020}]{liu2020reproductive}
Liu, Y., A.~A. Gayle, A.~Wilder-Smith, and J.~Rockl{\"o}v (2020).
\newblock {The reproductive number of COVID-19 is higher compared to SARS
  coronavirus}.
\newblock {\em J Travel Med\/}.

\bibitem[\protect\citeauthoryear{Ma, Dushoff, Bolker, and Earn}{Ma
  et~al.}{2014}]{ma2014estimating}
Ma, J., J.~Dushoff, B.~M. Bolker, and D.~J. Earn (2014).
\newblock Estimating initial epidemic growth rates.
\newblock {\em Bull Math Biol\/}~{\em 76\/}(1), 245--260.

\bibitem[\protect\citeauthoryear{Ma and Earn}{Ma and
  Earn}{2006}]{ma2006generality}
Ma, J. and D.~J. Earn (2006).
\newblock Generality of the final size formula for an epidemic of a newly
  invading infectious disease.
\newblock {\em Bull Math Biol\/}~{\em 68\/}(3), 679--702.

\bibitem[\protect\citeauthoryear{Majumder and Mandl}{Majumder and
  Mandl}{2020a}]{majumderncov}
Majumder, M. and K.~D. Mandl (2020a).
\newblock Early transmissibility assessment of a novel coronavirus in {Wuhan,
  China}.
\newblock \url{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3524675}.
  Accessed 27, January, 2020.

\bibitem[\protect\citeauthoryear{Majumder and Mandl}{Majumder and
  Mandl}{2020b}]{majumder2020early}
Majumder, M.~S. and K.~D. Mandl (2020b).
\newblock Early in the epidemic: impact of preprints on global discourse about
  {COVID-19} transmissibility.
\newblock {\em Lancet Glob Health\/}.

\bibitem[\protect\citeauthoryear{McBryde, Bergeri, van Gemert, Rotty, Headley,
  Simpson, Lester, Hellard, and Fielding}{McBryde
  et~al.}{2009}]{mcbryde2009early}
McBryde, E., I.~Bergeri, C.~van Gemert, J.~Rotty, E.~Headley, K.~Simpson,
  R.~Lester, M.~Hellard, and J.~E. Fielding (2009).
\newblock {Early transmission characteristics of influenza A (H1N1) v in
  Australia: Victorian state, 16 May--3 June 2009}.
\newblock {\em Euro Surveill\/}~{\em 14\/}(42), 19363.

\bibitem[\protect\citeauthoryear{Metcalf, Farrar, Cutts, Basta, Graham,
  Lessler, Ferguson, Burke, and Grenfell}{Metcalf
  et~al.}{2016}]{metcalf2016use}
Metcalf, C. J.~E., J.~Farrar, F.~T. Cutts, N.~E. Basta, A.~L. Graham,
  J.~Lessler, N.~M. Ferguson, D.~S. Burke, and B.~T. Grenfell (2016).
\newblock Use of serological surveys to generate key insights into the changing
  global landscape of infectious disease.
\newblock {\em Lancet\/}~{\em 388\/}(10045), 728--730.

\bibitem[\protect\citeauthoryear{Nishiura, Castillo-Chavez, Safan, and
  Chowell}{Nishiura et~al.}{2009}]{nishiura2009transmission}
Nishiura, H., C.~Castillo-Chavez, M.~Safan, and G.~Chowell (2009).
\newblock {Transmission potential of the new influenza A (H1N1) virus and its
  age-specificity in Japan}.
\newblock {\em Euro Surveill\/}~{\em 14\/}(22), 19227.

\bibitem[\protect\citeauthoryear{Nishiura and Chowell}{Nishiura and
  Chowell}{2015}]{nishiura2015theoretical}
Nishiura, H. and G.~Chowell (2015).
\newblock {Theoretical perspectives on the infectiousness of Ebola virus
  disease}.
\newblock {\em Theor Biol Med Model\/}~{\em 12\/}(1), 1.

\bibitem[\protect\citeauthoryear{Park, Champredon, Weitz, and Dushoff}{Park
  et~al.}{2019}]{park2019practical}
Park, S.~W., D.~Champredon, J.~S. Weitz, and J.~Dushoff (2019).
\newblock A practical generation-interval-based approach to inferring the
  strength of epidemics from their speed.
\newblock {\em Epidemics\/}~{\em 27}, 12--18.

\bibitem[\protect\citeauthoryear{Read, Bridgen, Cummings, Ho, and Jewell}{Read
  et~al.}{2020a}]{readncov}
Read, J.~M., J.~R. Bridgen, D.~A. Cummings, A.~Ho, and C.~P. Jewell (2020a).
\newblock {Novel coronavirus 2019-nCoV: early estimation of epidemiological
  parameters and epidemic predictions}.
\newblock \url{https://www.medrxiv.org/content/10.1101/2020.01.23.20018549v1}.
  Accessed 26, January, 2020.

\bibitem[\protect\citeauthoryear{Read, Bridgen, Cummings, Ho, and Jewell}{Read
  et~al.}{2020b}]{readncov2}
Read, J.~M., J.~R. Bridgen, D.~A. Cummings, A.~Ho, and C.~P. Jewell (2020b).
\newblock {Novel coronavirus 2019-nCoV: early estimation of epidemiological
  parameters and epidemic predictions}.
\newblock \url{https://www.medrxiv.org/content/10.1101/2020.01.23.20018549v2}.
  Accessed 5, February, 2020.

\bibitem[\protect\citeauthoryear{Riou and Althaus}{Riou and
  Althaus}{2020a}]{riouncov}
Riou, J. and C.~L. Althaus (2020a).
\newblock {Pattern of early human-to-human transmission of wuhan 2019-nCoV}.
\newblock \url{https://www.biorxiv.org/content/10.1101/2020.01.23.917351v1}.
  Accessed 26, January, 2020.

\bibitem[\protect\citeauthoryear{Riou and Althaus}{Riou and
  Althaus}{2020b}]{riou2020pattern}
Riou, J. and C.~L. Althaus (2020b).
\newblock {Pattern of early human-to-human transmission of Wuhan 2019 novel
  coronavirus (2019-nCoV), December 2019 to January 2020}.
\newblock {\em Euro Surveill\/}~{\em 25\/}(4), 2000058.

\bibitem[\protect\citeauthoryear{Roberts and Heesterbeek}{Roberts and
  Heesterbeek}{2007}]{roberts2007model}
Roberts, M. and J.~Heesterbeek (2007).
\newblock Model-consistent estimation of the basic reproduction number from the
  incidence of an emerging infection.
\newblock {\em J Math Biol\/}~{\em 55\/}(5-6), 803.

\bibitem[\protect\citeauthoryear{Roberts and Nishiura}{Roberts and
  Nishiura}{2011}]{roberts2011early}
Roberts, M.~G. and H.~Nishiura (2011).
\newblock {Early estimation of the reproduction number in the presence of
  imported cases: pandemic influenza H1N1-2009 in New Zealand}.
\newblock {\em PLoS One\/}~{\em 6\/}(5).

\bibitem[\protect\citeauthoryear{Sun, Chen, and Viboud}{Sun
  et~al.}{2020}]{sun2020early}
Sun, K., J.~Chen, and C.~Viboud (2020).
\newblock Early epidemiological analysis of the coronavirus disease 2019
  outbreak based on crowdsourced data: a population-level observational study.
\newblock {\em Lancet Dig Health\/}.

\bibitem[\protect\citeauthoryear{Svensson}{Svensson}{2007}]{svensson2007note}
Svensson, {\AA}. (2007).
\newblock A note on generation times in epidemic models.
\newblock {\em Math Biosci\/}~{\em 208\/}(1), 300--311.

\bibitem[\protect\citeauthoryear{Tariq, Roosa, Mizumoto, and Chowell}{Tariq
  et~al.}{2019}]{tariq2019assessing}
Tariq, A., K.~Roosa, K.~Mizumoto, and G.~Chowell (2019).
\newblock {Assessing reporting delays and the effective reproduction number:
  The Ebola epidemic in DRC, May 2018--January 2019}.
\newblock {\em Epidemics\/}~{\em 26}, 128--133.

\bibitem[\protect\citeauthoryear{Taylor, Dushoff, and Weitz}{Taylor
  et~al.}{2016}]{taylor2016stochasticity}
Taylor, B.~P., J.~Dushoff, and J.~S. Weitz (2016).
\newblock Stochasticity and the limits to confidence when estimating
  $\mathcal{R}_0$ of {Ebola} and other emerging infectious diseases.
\newblock {\em J Theor Biol\/}~{\em 408}, 145--154.

\bibitem[\protect\citeauthoryear{Tian, Liu, Li, Wu, Chen, Kraemer, Li, Cai, Xu,
  Yang, Wang, Yang, Cui, Song, Zheng, Wang, Bjornstad, Yang, Grenfell, Pybus,
  and Dye}{Tian et~al.}{2020}]{Tianeabb6105}
Tian, H., Y.~Liu, Y.~Li, C.-H. Wu, B.~Chen, M.~U.~G. Kraemer, B.~Li, J.~Cai,
  B.~Xu, Q.~Yang, B.~Wang, P.~Yang, Y.~Cui, Y.~Song, P.~Zheng, Q.~Wang, O.~N.
  Bjornstad, R.~Yang, B.~T. Grenfell, O.~G. Pybus, and C.~Dye (2020).
\newblock An investigation of transmission control measures during the first 50
  days of the covid-19 epidemic in china.
\newblock {\em Science\/}.

\bibitem[\protect\citeauthoryear{Trichereau, Verret, Mayet, Manet, Decam,
  Meynard, Deparis, and Migliani}{Trichereau
  et~al.}{2012}]{trichereau2012estimation}
Trichereau, J., C.~Verret, A.~Mayet, G.~Manet, C.~Decam, J.-B. Meynard,
  X.~Deparis, and R.~Migliani (2012).
\newblock {Estimation of the reproductive number for A (H1N1) pdm09 influenza
  among the French armed forces, September 2009--March 2010}.
\newblock {\em J Infect\/}~{\em 64\/}(6), 628--630.

\bibitem[\protect\citeauthoryear{Wallinga and Lipsitch}{Wallinga and
  Lipsitch}{2007}]{wallinga2007generation}
Wallinga, J. and M.~Lipsitch (2007).
\newblock How generation intervals shape the relationship between growth rates
  and reproductive numbers.
\newblock {\em Proc R Soc Lond B Biol Sci\/}~{\em 274\/}(1609), 599--604.

\bibitem[\protect\citeauthoryear{Wearing, Rohani, and Keeling}{Wearing
  et~al.}{2005}]{wearing2005appropriate}
Wearing, H.~J., P.~Rohani, and M.~J. Keeling (2005).
\newblock Appropriate models for the management of infectious diseases.
\newblock {\em PLoS Med\/}~{\em 2\/}(7).

\bibitem[\protect\citeauthoryear{{World Health Organization}}{{World Health
  Organization}}{2020a}]{who112}
{World Health Organization} (2020a).
\newblock {Coronavirus disease 2019 (COVID-19) Situation Report - 112}.
\newblock
  \url{https://www.who.int/docs/default-source/coronaviruse/situation-reports/20200511-covid-19-sitrep-112.pdf?sfvrsn=813f2669_2}.
  Accessed May 11, 2020.

\bibitem[\protect\citeauthoryear{{World Health Organization}}{{World Health
  Organization}}{2020b}]{who17protocol}
{World Health Organization} (2020b).
\newblock {Laboratory testing for 2019 novel coronavirus (2019-nCoV) in
  suspected human cases}.
\newblock
  \url{https://www.who.int/publications-detail/laboratory-testing-for-2019-novel-coronavirus-in-suspected-human-cases-20200117}.
  Accessed February 4, 2020.

\bibitem[\protect\citeauthoryear{{World Health Organization}}{{World Health
  Organization}}{2020c}]{pneumonia}
{World Health Organization} (2020c).
\newblock Pneumonia of unknown cause -- {China}.
\newblock
  \url{https://www.who.int/csr/don/05-january-2020-pneumonia-of-unkown-cause-china/en/}.
  Accessed January 30, 2020.

\bibitem[\protect\citeauthoryear{Wu, Leung, and Leung}{Wu
  et~al.}{2020}]{wu2020nowcasting}
Wu, J.~T., K.~Leung, and G.~M. Leung (2020).
\newblock {Nowcasting and forecasting the potential domestic and international
  spread of the 2019-nCoV outbreak originating in Wuhan, China: a modelling
  study}.
\newblock {\em Lancet\/}.

\bibitem[\protect\citeauthoryear{Zhao, Lin, Ran, Musa, Yang, Wang, Lou, Gao,
  Yang, He, et~al.}{Zhao et~al.}{2020}]{zhao2020preliminary}
Zhao, S., Q.~Lin, J.~Ran, S.~S. Musa, G.~Yang, W.~Wang, Y.~Lou, D.~Gao,
  L.~Yang, D.~He, et~al. (2020).
\newblock {Preliminary estimation of the basic reproduction number of novel
  coronavirus (2019-nCoV) in China, from 2019 to 2020: A data-driven analysis
  in the early phase of the outbreak}.
\newblock {\em Int J Infect Dis\/}.

\bibitem[\protect\citeauthoryear{Zhao, Ran, Musa, Yang, Lou, Gao, Yang, and
  He}{Zhao et~al.}{2020}]{zhaoncov}
Zhao, S., J.~Ran, S.~S. Musa, G.~Yang, Y.~Lou, D.~Gao, L.~Yang, and D.~He
  (2020).
\newblock {Preliminary estimation of the basic reproduction number of novel
  coronavirus (2019-nCoV) in China, from 2019 to 2020: A data-driven analysis
  in the early phase of the outbreak}.
\newblock \url{https://www.biorxiv.org/content/10.1101/2020.01.23.916395v1}.
  Accessed 26, January, 2020.

\end{thebibliography}
